### 2015-07-05 narrative/intro.tex
minor edits to the introduction

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time knowledge" from 
scientific computing, aligns perfectly this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

Our approach targets the expected characteristics of exascale storage hardware.
The storage layer will be partitioned into multiple heterogeneous tiers with
vastly different performance characteristics. The layers will be further
differentiated by the constraints on capacity and data lifetime within each
layer. Tape archival storage will still maintain data long term, but access to
this data will be orders of magnitude slower than the next layer and naively
accessing data from archival storage will greatly impact productivity.
%
Our approach in this proposal is to enable researchers to place more knowledge
into the SSIO system so that data can be recast from a bunch of bytes to
information, which the system can then place and optimize the time to gain
knowledge from exascale simulations.  We first motivate this by a problem our
team has been working on in the past six months, and then recast this problem
into a series of research questions and challenges which must be addressed in
order to optimize the SSIO system for exascale science.

The traditional approach to transforming results of scientific computation into
knowledge consists of storing the numerical output of a simulation on disk,
followed by a post-processing or analysis stage that might take place over
several ensuing weeks or months. The overarching objective is to gain insight,
or knowledge.  As already mentioned, the anticipated scale of computations
means that this workflow is simply no longer viable.
%
\section{Scalable Storage Software Infrastructure}
Our focus in this proposal is in theme 2: Scalable Storage Software Infrastructure. We will focus on a state of the art
SSIO solution to solve problems which researchers are beginning to face and will make science on exascale systems
problematic without new insights and solutions.

>>>>

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time knowledge" from 
scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

Our approach targets the expected characteristics of exascale storage hardware.
The storage layer will be partitioned into multiple heterogeneous tiers with
vastly different performance characteristics. The layers will be further
differentiated by the constraints on capacity and data lifetime within each
layer. Tape archival storage will still maintain data long term, but access to
this data will be orders of magnitude slower than the next layer and naively
accessing data from archival storage will greatly impact productivity.
%
Our approach in this proposal is to enable researchers to place more knowledge
into the SSIO system so that data can be recast from a sequence of bytes to
information, which the system can then place and optimize the time to gain
knowledge from exascale simulations.  We first motivate this by a problem our
team has been working on in the past six months, and then recast this problem
into a series of research questions and challenges which must be addressed in
order to optimize the SSIO system for exascale science.

The traditional approach to transforming results of scientific computation into
knowledge consists of storing the numerical output of a simulation on disk,
followed by a post-processing or analysis stage that might take place over
several ensuing weeks or months. Clearly, given the computation expected at the
exascale, this type of workflow is simply not viable.

%
\section{Scalable Storage Software Infrastructure}
Our focus in this proposal is in theme 2: Scalable Storage Software Infrastructure. We will focus on a state of the art
SSIO solution to solve problems which researchers are beginning to face and will make science on exascale systems
problematic without new insights and solutions.
